### 2019-09-27 budget.tex

\hspace{-4cm}
  \begin{tabular}{clcrccccr}
     & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost} \\ \hline\hline

@@

     &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline\hline

>>>>

\hspace{-1cm}
  \begin{tabular}{|clcrccccr|}
    \hline
     & \multicolumn{1}{c}{Item} & \multicolumn{1}{c}{Priority} & \multicolumn{1}{c}{Cost Per Unit} & \multicolumn{1}{c}{Thursday} & \multicolumn{1}{c}{Friday} & \multicolumn{1}{c}{Saturday} & \multicolumn{1}{c}{General} & \multicolumn{1}{c}{Total Cost} \\ \hline\hline

@@

     &                           &                           &                           &                           &                          &                           &                           &                          \\ \hline
